### 2015-09-24 README.Rmd
added code of conduct

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`

>>>>

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
